Network Cascades

### 2016-08-25 paper/paper.tex
Describe what a successful cascade is

>>>>

The model is then simulated over time until a steady state is reached. That is, the point where the entire system is stable and no agent will ever change its state again. The case of a steady state is easily verifiable: if all agents have observed their neighbors at least once since the last time any agent changed its state, then further observations will always lead to the same repeated result of no agent changing its state anymore. At this point, the simulation is finished.

After the simulation is done, there can be two results: either the experiment was successful and a global cascade has occurred, or the experiment has failed and the cascade was too small to be considered global.

What exactly constitutes as a successful global cascade is defined by $\frac{\textmd{Number of agents}}{\textmd{Agents in state } 1} \geq T$, where $T \in [0, 1]$ is some arbitrarily chosen threshold value. For example, $T = 1$ would require every last agent to have changed its state to $1$, which is difficult to achieve in a large random graph. A value like $T = 0.9$ would only require a 90\% majority, but still intuitively result in a cascade that was ``sufficiently global''.
